\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.5in,footskip=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage[OT1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\RequirePackage{ifthen}
\usepackage{parallel}
\usepackage{blindtext}

\newcommand{\lang}[2]{\begin{Parallel}{9cm}{9cm}\ParallelLText{#1}\ParallelRText{#2}\ParallelPar \end{Parallel}}
\newcommand{\ai}[2]{
	\lang{
		\texttt{#1}
	}{
		\texttt{#2}
	}
}

\newcommand{\ainame}{AI NAME GOES HERE}
\newcommand{\mainname}{MAIN CHAR NAME GOES HERE}
\newcommand{\auxname}{SIDEKICK CHAR NAME GOES HERE}
\newcommand{\corpname}{COMPANY NAME GOES HERE}
\newcommand{\ceoname}{CEO NAME GOES HERE}

\begin{document}
\lang{Text in Russian goes here}{Text in English will go here}
\lang{Text in Russian goes here}{Text in English shall go here}
\iffalse
Main idea for text: explore what happens if executive meddling is invoked on important technology (like internet is being broken by governments everywhere)

Story outline: 
tech inventor makes tech
some influencer (govt, CEO, ...) tries to manipulate tech in order to serve some (not-public) interest
(inventor must think manipulation is good)
influencer causes tech to have modification that serves non-public interest
original creator breaks tech (TODO: add some choice of whether to break; keeping it must have benefit)
people are unhappy when tech is modified, but less so when tech broken
people independetly clone tech, so influencer incapable of controlling it

Specifics:
- tech is voice-activated AI, controls (pre-existing) connected devices 
- influencer is president of country, controls by laws
- modification is surveillance and automatic reporting (for reasons of law enforcement)
%- reason it is broken is false triggering (that cannot be fixed: see https://www.theregister.co.uk/2017/11/17/its_artificial_its_intelligent_its_in_my_home_and_its_gone_bonkers/)

\fi

\ai{...}{Initializing... System online.}
\lang{...}{``Oh good, it's finally booted. \ainame, what is seven plus eight?''}
\ai{...}{Seven plus eight is five thousand seventy four point nine nine nine nine nine nine ni- Shutting down.}
\lang{...}{``What the... Right, who broke the build?'' \mainname yelled, getting up from his desk.}
\lang{...}{``I just pushed a new version out on the backend, you might want to download the new firmware version,'' he heard \auxname say from behind the server rack.}
\lang{...}{``Ah, so it is. Okay, let me just do that real quick,'' said \mainname, and in a moment, every screen in the office switched over to showing a pretty spinning wheel as the word "\texttt{DOWNLOADING}" appeared on every surface.}
\lang{...}{Ordinarily, such a major interruption would halt all work for the day, as everyone in the office rushed to the pub for an extended lunch break. But as \mainname walked over to the vending machine, he looked around the office, trying to count how many people were in today.}
\lang{...}{``Seven. That's 2 weeks in a row.''}
\lang{...}{Despite \corpname's reputation as the leading provider of connected household technolody, its profit margins left a lot to be desired. Sales have been down for the last 2 years, mostly because cheaper, simpler alternatives to their products have become widely available. Despite what \ceoname, the company's CEO, would have you believe, not everyone wants an autonomous drone for food delivery.}
\lang{...}{``Okay, good work everybody. Let's have a round of drinks on the house!'' said \mainname, loading up the drone with soda cans. As it flew off over the empty cubicles, he remembered that one of their competitors, TransCorp, has decided to use military assault robots as a cost-cutting measure. At least it didn't come to that here, he thought, although he wouldn't put it past \ceoname.}
\lang{...}{Now this new product, \ainame, is supposed to fix all the company's problems. While a \corpname-branded microwave oven, or window, or doorbell, is technically a connected device, when there is nothing to connect to, it just works like a normal appliance. But in the presence of \ainame, you only need to say what you want to be done and the AI will use all your \corpname devices to do so. Meaning you just say that you want to watch a movie, and right away the popcorn is ready, the lights are dimmed, and your TV is ready to play.}
\lang{...}{That's the theory, anyway. With the project being so understaffed, it becomes more about waiting for the device -- itself resembling a soda can -- to boot, connect to \auxname's servers, and then claim that seven plus eight is five thousand seventy four point nine nine nine nine nine nine. That alone would not be so bad, except you just know the CEO's going to come in and say --}



\end{document}
